A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-05-23 intro.tex
adding citations, history

Integrated Assessment Models (IAMs) are tools used to understand the complex
interactions between energy systems, economoic systems, land use, the climate,
and air pollution, among other sectors \cite{van_vuuren_energy_2017,
  kriegler_fossil-fueled_2017, calvin_ssp4:_2017, fujimori_ssp3:_2017,
  fricko_marker_2017}. IAMs provide global projections of systemic change by
dividing the world into a number of representative regions, the definition of
which is distinct for each model. Results from IAMs are integral in a number of
international studies, which notably include projections of climate and economic
futures used in analyses underpinning the Intergovenmental Panel on Climate
Change (IPCC) \TODO{cite} and the United Nations Framework Convention on Climate
Unchange (UNFCCC)'s Paris Agreement \TODO{cite}.

@@

With some frequency, however, historical data is updated to incorporate new
assumptions of source activity, new emissions accounting practices, or other
concerns. The global climate change community has recently updated a standard
historical emissions dataset for both anthropogenic and land-use change
emissions \TODO{cite ceds and LUC paper} as part of the 6th phase of the Coupled
Model Intercomparison Project \TODO{cite cmip6} (CMIP6). These historical
emissions trajectories in conjunction with future trajectories as provided by
IAMs are critical inputs to the climate-related modeling exercises of CMIP6.

>>>>

Integrated Assessment Models (IAMs) are tools used to understand the complex
interactions between energy systems, economoic systems, land use, the climate,
and air pollution, among other sectors \cite{van_vuuren_energy_2017,
  kriegler_fossil-fueled_2017, calvin_ssp4:_2017, fujimori_ssp3:_2017,
  fricko_marker_2017}. IAMs provide global projections of systemic change by
dividing the world into a number of representative regions, the definition of
which is distinct for each model. Results from IAMs are integral in a number of
international studies, which notably include projections of climate and economic
futures used in analyses underpinning the Intergovenmental Panel on Climate
Change (IPCC) and the United Nations Framework Convention on Climate Unchange
(UNFCCC)'s Paris Agreement \TODO{cite}.

@@

With some frequency, however, historical data is updated to incorporate new
assumptions of source activity, new emissions accounting practices, or other
concerns. The global climate change community has recently updated a standard
historical emissions dataset for both anthropogenic and land-use change
emissions \cite{hoesly_historical_2017,van_marle_historic_2017} as part of the
6th phase of the Coupled Model Intercomparison Project \TODO{cite cmip6}
(CMIP6). These historical emissions trajectories in conjunction with future
trajectories as provided by IAMs are critical inputs to the climate-related
modeling exercises of CMIP6.
